\subsection{Attributions}\label{attributions}

This book is dedicated to the public domain and licensed under the terms
of the \href{license.html}{CC0 license}.

\textbf{Book Publishing}: Clément Renaud

\textbf{Cover Painting}: Omar Ibrahim, artist born in the south of Syria
1978, living and working in Paris.

\textbf{Book Production and Cover Design}: Julien Taquet

\textbf{Book Sprint Facilitation}: Barbara Rühling

\textbf{Text Clean-Up}: Raewyn Whyte

\textbf{MISSINGBASSEL Illustration}: Neil Stuber

\subsection{Contributors}\label{contributors}

\protect\hypertarget{christopher-adams}{}{}Christopher Adams is 35 years
old. He is a photographer, and published
\href{http://freesouls.cc}{FREESOULS} by JOI ITO. Christopher is a
member of \href{https://fabricatorz.com}{Fabricatorz} and helps run the
\href{http://freebassel.org}{\#FREEBASSEL} campaign. He lives in Taipei.

\protect\hypertarget{sabrina-banes}{}{}Sabrina Banes
(@\href{https://twitter.com/missbananabiker}{missbananabiker}) writes
about information security, web freedoms, strong cryptography, anarcho-
communism.

\protect\hypertarget{the-big-conversation-space}{}{}By The Big
Conversation Space (Niki Korth \& Clémence de Montgolfier) is an art and
research collaborative dedicated to conversations of all shapes, sizes,
and (file) formats.

\protect\hypertarget{tim-boykett}{}{}Tim Boykett is involved in
researches in the field of nearrings, relations between theoretical
computer science and abstract algebra.

\protect\hypertarget{lorna-campbell}{}{}Lorna Campbell work for the
University of Edinburgh. She is specialized in open education
technology, policy, and practice.

\protect\hypertarget{giorgos-cheliotis}{}{}Giorgos Cheliotis lives and
works in Athens. He is a close observer of networks, internet cultures,
sociotechnical and policy issues in new media.

\protect\hypertarget{tyng-ruey-chuang}{}{}Tyng-Ruey Chuang led Creative
Commons Taiwan. His research areas include functional programming,
programming languages and systems, XML and Web technologies, and social
implications of information technologies.

\protect\hypertarget{ginger-coons}{}{}ginger coons is a digital
researcher, a f-loss design advocate, and editor of
@\href{https://twitter.com/libgraphicsmag}{libgraphicsmag}.

\protect\hypertarget{ben-dablo}{}{}Ben Dablo is a 31 year old citizen
wanderer living in Portland, Oregon.

\protect\hypertarget{georges-dahdouh}{}{}Georges Dahdouh is a 37 years
old Syrian designer and 3D artist. He is located in Dubai.

\protect\hypertarget{patrick-w-deegan}{}{}Patrick W. Deegan is a
researcher, focus on new media art practice, sociology, and ethics. He
is also a freelance curator and developer at
\href{https://fabricatorz.com/}{Fabricatorz}.

\protect\hypertarget{martin-paul-eve}{}{}Dr.~Martin Paul Eve is a senior
lecturer in literature, technology and publishing. He lives in London.

\protect\hypertarget{pauline-gadea}{}{}Pauline Gadea is 30 years old.
She lives in Toulouse. After years in the media, Pauline now works in
local food craft products.

\protect\hypertarget{lucas-gonze}{}{}Lucas Gonze is a product innovator,
hacker, creative technologist.

\protect\hypertarget{richard-goodman}{}{}Richard Goodman is the
E-Learning Systems Team Manager in IT Services at Loughborough
University.

\protect\hypertarget{shauna-gordon-mckeon}{}{}Shauna Gordon-McKeon is a
U.S. writer, independent researcher and developer. She focuses on open
technologies and communities.

\protect\hypertarget{christian-grothoff}{}{}Christian Grothoff is
maintainer of \href{https://taler.net}{GNU Taler}.

\protect\hypertarget{hellekin}{}{}A global nomad,
\href{https://twitter.com/hellekin}{hellekin} is a free software
activist, member of the \href{https://dyne.org}{Dyne.org} Foundation,
and \href{https://gnu.org/consensus}{GNU consensus} maintainer.

\protect\hypertarget{adam-hyde}{}{}Adam Hyde is the founder of
\href{http://booksprints.net}{BookSprints}.

\protect\hypertarget{pete-ippel}{}{}Pete Ippel's art is conceptual in
nature and spans a variety of media from the traditional to the cutting
edge. Pete's personal account is
@\href{https://twitter.com/hypermodern}{hypermodern}.

\protect\hypertarget{jaromil}{}{}Jaromil is a member of the
\href{http://www.dyne.org}{Dyne.org} Foundation and the
\href{http://dcentproject.du}{D-CENT} project.

\protect\hypertarget{muid-latif}{}{}Muid Latif is a Malaysian-based web
designer, graphic designer and digital artist.

\protect\hypertarget{lawrence-lessig}{}{}Lawrence Lessig is an American
academic, and political activist. He is the founder of
\href{http://creativecommons.org/}{Creative Commons} and
\href{http://www.rootstrikers.org/}{Rootstrikers}.

\protect\hypertarget{yu-li}{}{}Yu Li is 31 years old. She lives and
works between Geneva and Shenzhen. Yu is a researcher, interaction and
speculative designer.

\protect\hypertarget{mike-linksvayer}{}{}Mike Linksvayer is a dilettante
of various free knowledge movements and a sub-dilettante critic of the
same.

\protect\hypertarget{geert-lovink}{}{}Geert Lovink is a Dutch-Australian
media theorist and critic. He is the founding director of the Institute
of Network Cultures, Amsterdam.

\protect\hypertarget{sulaiman-majali}{}{}Sulaïman Majali is an artist
based in Glasgow, Scotland. His works question the relationships between
the sculptural object and the photographic image in the mythologies of
our imagined communities.

\protect\hypertarget{jean-noel-montagne}{}{}Jean Noël Montagné, founder
of a hackerspace in Nice, France, called Nicelab, ``Open Laboratory of
Nice''.

\protect\hypertarget{jon-phillips}{}{}Jon Phillips is the co-founder of
design and technology company
\href{https://fabricatorz.com}{Fabricatorz}. He lives in Hong Kong. Jon
founded the \href{http://freebassel.org/}{\#FREEBASSEL} campaign in
2012. Transcript by Ekta Saran.

\protect\hypertarget{theophile-pillault}{}{}Théophile Pillault is 33
years old. He lives in Marseille. Théophile is a freelance journalist,
working for Vice, Les Inrockuptibles or Trax Magazine.

\protect\hypertarget{radium}{}{}radium is a member of the
\href{http://www.dyne.org}{Dyne.org} Foundation and the
\href{http://dcentproject.du}{D-CENT} project.

\protect\hypertarget{donatella-della-ratta}{}{}Donatella Della Ratta has
been managing the Creative Commons Arab world community for five years.
She maintains a blog on Arab media at \url{http://mediaoriente.com} and
tweets avidly @\href{https://twitter.com/donatelladr}{donatelladr}.

\protect\hypertarget{clement-renaud}{}{}\href{http://clementrenaud.com}{Clément
Renaud} is a 32-years old researcher, developer, creative coder, and
journalist based in Lyon.

\protect\hypertarget{faraj-rifait}{}{}Faraj Rifait is Bassel's uncle.

\protect\hypertarget{melanie-dulong-de-rosnay}{}{}Mélanie Dulong de
Rosnay is a researcher at french institution CNRS Institute for
Communication Sciences where she is in charge of the Information and
Commons Governance research group.

\protect\hypertarget{natacha-roussel}{}{}Natacha Roussel is a f-loss
artist. She is the co-founder of the F-lat collective. Natacha is based
in Brussels.

\protect\hypertarget{noura-ghazi-safadi}{}{}Noura Ghazi Safadi is a
Syrian writer. She's married to Bassel.

\protect\hypertarget{anasuya-sengupta}{}{}Anasuya Sengupta is an
advocate, strategist, and storyteller, currently on the Board of
Directors of the Nonprofit Quarterly, an online and print publication
that promotes an active and engaged democracy. She previously headed the
Grantmaking department at the Wikimedia Foundation, and the Asia Pacific
portfolio at the Global Fund for Women.

\protect\hypertarget{barry-threw}{}{}Designer, technologist, and
apparently author, \href{http://www.barrythrew.com/}{Barry Threw}
(@\href{https://twitter.com/barrythrew}{barrythrew}) is the Director of
Software at \href{http://www.obscuradigital.com/}{Obscura Digital},
curator with \href{http://www.grayarea.org/}{Gray Area} Foundation for
the Arts, and the Interim Director of the \href{}{\#NEWPALMYRA} project.
He lives in San Francisco, CA.

\protect\hypertarget{stephanie-vidal}{}{}Stéphanie Vidal is 30 years
old. She is a cultural journalist specialised in new media and digital
strategist. Stéphanie lives in Paris.

\protect\hypertarget{marc-weidenbaum}{}{}Marc Weidenbaum publishes a
webzine, Disquiet, about electronic ambient music and has contributed to
the scientific journal Nature upon this subject. He was editor-in-chief
for two of Viz Media's magazines. He lives in San Francisco.

\protect\hypertarget{john-wilbanks}{}{}John Wilbanks is the Chief
Commons Officer at Sage Bionetworks and a Senior Fellow at the Ewing
Marion Kauffman Foundation and at FasterCures. He ran the Science
Commons project at Creative Commons.

\protect\hypertarget{maarten-zeinstra}{}{}Maarten Zeinstra is an advisor
copyright law and technology in the cultural sector for Nederlands
agency Kennisland. He lives in Amsterdam.

\protect\hypertarget{mushon-zer-aviv}{}{}Mushon Zer-Aviv is a designer,
an educator and a media activist. He is based in Tel Aviv.

\protect\hypertarget{ethan-zuckerman}{}{}Ethan Zuckerman, Director,
Center for Civic Media, MIT Media Lab, where Bassel was
\href{http://joi.ito.com/weblog/2015/10/22/mit-media-lab-r.html}{offered
a researcher position} on October 22, 2015.
