\subsection{Online Resources}\label{online-resources}

This book only scratched the surface of what's being done in the free
culture movements around the world. It is a call to action. The authors
invite interested readers to explore these topics on the Web, and
participate in like-minded projects in their area. A collection of
relevant links is available at \url{http://costoffreedom.cc/links.html}.

Bassel tweeted as {[}@basselsafadi{]}(https://twitter.com/basselsafadi)
from 2008. A full transcript of his tweets up to his arrest on March,
15, 2012, is available at \url{http://costoffreedom.cc/bassel-tweets/}.
You may also want to follow
{[}@freebassel{]}(https://twitter.com/freebassel) and
@\href{https://twitter.com/costfreedombook}{costfreedombook} on Twitter.
The \href{https://twitter.com/hashtag/freebassel}{\#freebassel} and
\href{https://twitter.com/hashtag/costoffreedom}{\#costoffreedom}
hashtags are used for sharing related contents.

We'd love to hear from you! You can join a mailing-list:
\href{mailto:book-subscribe@costoffreedom.cc}{book@costoffreedom.cc}. A
low-traffic announcement list suitable for journalists is also available
at
\href{mailto:cof-announce-subscribe@lists.costoffreedom.cc}{announce@costoffreedom.cc}.

You may find us idling on the
\href{http://freenode.net/using_the_network.shtml}{Freenode} IRC
network, on the channel
\href{http://web.freenode.net/\#costoffreedom}{\#costoffreedom}.

Thank you for your attention.
\href{http://freebassel.org/}{\#FREEBASSEL}
